FoRTE baseline

### 2019-03-25 analysis/paper/paper.Rmd
[paper] Add minor notes about RTM and crown model

<!-- Add something positive about each of these? Then, the section about models is more compelling. -->
In trying to anticipate future changes to terrestrial ecosystems, ecologists have four general techniques.
One approach is to look to the past to see how ecosystems responded to similar changes (REFs).
This is challenging for two reasons:
For one, we often have to look very far back to find similar climate changes, and the techniques we have for determining the state of ecosystems in the distant past have limited detail (REF).
More importantly, there are few (if any) times where the climate has changed as rapidly as it is now, and it is unclear whether slower changes in the past will trigger responses similar to the faster changes happening now (REF).
A second approach is space-for-time substitution, whereby we use existing climatic gradients through space (e.g. with latitude or elevation) to infer the corresponding changes through time (REF).
However, many processes that drive spatial variation in ecosystems play out over hundreds or thousands of years (e.g. evolution), far longer than policy-relevant timescales of years to decades and far slower than the current pace of climate change (REF).
A third approach is to conduct experimental manipulations, where individuals are subjected to controlled changes in environmental conditions [@medlyn_2015_using].
Because they are able to isolate specific changes by controlling for most other factors, experiments are very useful for testing mechanisms.
Unfortunately, resource constraints limit the spatial and temporal extent of experiments, and emerging evidence from (the relatively few) long-term experiments suggests that short-term results cannot always be extrapolated from longer-term results [@reich_2018_unexpected].

@@

- Radiative transfer
  - Two-stream model
    - Same general approach as in CLM 4.5 [@clm45_note], but rather than solving for just two layers (sunlit and shaded), solve for each canopy layer.
    - Set up the two-stream equations for each layer as a linear system and solve the entire set of equations numerically
    - Similar to approaches used in other models: JULES [@mercado_2007_improving], ORCHIDEE-CAN [@naudts_2015_vertically], CLM(SPA) [@bonan_2014_modeling]
  - Multiple scatter model **TODO**

>>>>

<!-- Add something positive about each of these? Then, the section about models is more compelling. -->
In trying to anticipate future changes to terrestrial ecosystems, ecologists have four general techniques.
One approach is to look to the past to see how ecosystems responded to similar changes (REFs -- e.g. PALEON?).
This is challenging for two reasons:
For one, we often have to look very far back to find similar climate changes, and the techniques we have for determining the state of ecosystems in the distant past have limited detail (REF).
More importantly, there are few (if any) times where the climate has changed as rapidly as it is now, and it is unclear whether slower changes in the past will trigger responses similar to the faster changes happening now (REF).
A second approach is space-for-time substitution, whereby we use existing climatic gradients through space (e.g. with latitude or elevation) to infer the corresponding changes through time (REF).
However, many processes that drive spatial variation in ecosystems play out over hundreds or thousands of years (e.g. evolution), far longer than policy-relevant timescales of years to decades and far slower than the current pace of climate change (REF).
A third approach is to conduct experimental manipulations, where individuals are subjected to controlled changes in environmental conditions [@medlyn_2015_using].
Because they are able to isolate specific changes by controlling for most other factors, experiments are very useful for testing mechanisms.
Unfortunately, resource constraints limit the spatial and temporal extent of experiments, and emerging evidence from (the relatively few) long-term experiments suggests that short-term results cannot always be extrapolated from longer-term results [@reich_2018_unexpected].

@@

- Radiative transfer
  - Two-stream model (ED default)
    - Same general approach as in CLM 4.5 [@clm45_note], but rather than solving for just two layers (sunlit and shaded), solve for each canopy layer.
    - Set up the two-stream equations for each layer as a linear system and solve the entire set of equations numerically
    - Similar to approaches used in other models: JULES [@mercado_2007_improving], ORCHIDEE-CAN [@naudts_2015_vertically], CLM(SPA) [@bonan_2014_modeling]
  - Multiple scatter model
    - Based on @zhao_2005_multiple
- Crown model
  - Infinite (ED2 default)
    - Marginally taller cohorts completely shade out shorter ones
  - Finite
    - Cohorts have a finite crown area, so multiple cohorts have access to the same light level
    - Based on crown area allometries from @dietze_2008_changing
- Trait plasticity
